\bckg{Assets/bbg2}

\poemtitle{Farewell Friend}
%%
\begin{verse}
`Inco is my best friend! Inco sent me this one last letter.'
\end{verse}

\begin{verse}
- Chorus - \\
Hide from the sun \\
I'll never return \\
Run to planet Nl-21 \\
They get their guns \\
To make things fun \\
Planet code name NL-21
\end{verse}

\begin{verse}
We love Planet NL-21
\end{verse}

\begin{verse}
I met you on the hill \\
You were lost and afraid \\
The same hill that became, our own secret new place \\
The place for the start of an undying quest \\
Uncovering the truth they were hiding too well \\
The sweetest and bravest one I ever met \\
You said, you would do anything for a friend \\
I'll never forget a single moment \\
But now is the time for me to fly away \\
I'll be fine, you will survive \\
We will meet in next life \\
When, peace has come back to this place \\
I miss you, I love you \\
I'm sorry for lying again \\
But I'm still your friend
\end{verse}

\clearpage
\bckg{Assets/bbg2}

\begin{verse}
- Chorus -
\end{verse}

\begin{verse}
Sombrer n'est pas si mal  \\
Quand la nuit va me libérer \\
Le soleil n'est qu'illusoire \\
Je saurai le créer le ciel sera à notre image \\
骄阳似火 \\ 
Only in our wildest dreams \\
Sans connaître de limite \\
There will be no place for fear
\end{verse}

\begin{verse}
We travel by day and attack at night \\
They won't see us coming we're out of sight \\
The planet is ours, we start building towers \\
And streets filled with concrete
\end{verse}

\begin{verse}
Farewell my friend, no more summer letters \\
The fun we had couldn't last forever  \\
辞旧迎新 only getting better \\
Dernier vestige, my summer letter
\end{verse}

\begin{verse}
There's so much more I cannot show \\ 
So many things I wanna say \\
Don't lose your hope even when you fall \\
When darkness is only what you see \\
Farewell my friend, no more summer letters \\
No summer letters
\end{verse}

\clearpage
\bckg{Assets/bbg2}

\begin{verse}
And we orbit around NL-21 \\ 
A planet without a sun \\ 
When we enter the atmosphere \\ 
Darkness disappears \\ 
How this could happen \\ 
How these things could be true \\ 
No matter where we go \\ 
We'll stick together like glue
\end{verse}

\begin{verse}
Look! Are you seeing this? The planet itself is glowing!\\ 
I see it too! It's glowing! \\ 
Cheese! Oh and honey! \\ 
Look at the trees! Is there anyone here? \\ 
Sshh... I can hear something! 
\end{verse}

\begin{verse}
We're discovering new galaxies \\ 
So that humanity gets more capacities \\ 
There will be casualties with alien families  \\ 
We're taking care of that pretty casually \\ 
There's cheese on trees and bottles of wine \\ 
Growing on them like a vine \\ 
Rivers filled with honey \\ 
No need for money \\ 
Come together let us dine \\ 

We travel by day and attack at night \\ 
They won't see us coming we're out of sight \\ 
The planet is ours, we start building towers \\ 
And streets filled with concrete
\end{verse}

\clearpage
