\bckg{Assets/bbg2}

\poemtitle{Party Planet}
%%
\begin{verse}
I can't believe that I got away with it this time! \\
I've got a core! Fun will soon be restored... \\
Will Cosmoose notice that this AI brain is no longer \\
(I've got a core)  \\
In their care? \\
(Fun will soon be restored)
\end{verse}

\begin{verse}
Core 7C, it calls to me \\
Blue and swirling \\
Positronic destiny! \\
One minor tweak  \\
And in just one week \\
16 Cyg B will be Planet Party! \\
Core 7C \\
(Yes Miss Fox?)\\
Let's go, baby!
\end{verse}

\clearpage
\bckg{Assets/bbg2}

\begin{verse}
Driving me insane \\
Time to find out where she went \\

You will never get it back from me, my friend, \\
But you are invited to the party, Florrie! \\
(Oh there she is!) \\
But sick beats will play from every tree, \\
The dance floor will stretch as far as the eye can see... \\
(You can't do this) \\
(That's not what 7C is for) \\
(Maar het wordt een leuk feestje hoor!) \\
This core is called the Seven Seas  \\
You don't understand her story \\
パーティーしよう!
\end{verse}


\begin{verse}
Oh no, she's on my tail! \\
Full speed so Planet Party can prevail! \\
I'll hack this AI core and \\
Pretty soon we'll all meet on the dance floor \\
With games galore!
\end{verse}


\begin{verse}
Just imagine, party heaven! \\
Games and emcees! Join me, Florrie!
\end{verse}

\clearpage
\bckg{Assets/bbg2}

\begin{verse}
Seven Seas are you ok? Can you hear me? \\
このパーティーは すごい!! Oh Florrie, ca va?  \\
Oh no, she's reprogramming you! But I'll save you! \\
This core is called the Seven Seas  \\
You will never understand the whole story \\
Sometimes it's hard to party \\
Running after somebody \\
But 7Cs will be back and safe with me \\
Thank you, Florrie, I didn’t mean to make you worry 
\end{verse}

\begin{verse}
Oh no there it goes up in her tractor beam Core \\
Seven Cs is now just a dream \\
We will party no more \\
Goood-Goodbye AI core \\
Back to sailing the Kuiper belt but yes, you will see me once more... 
\end{verse}

\clearpage
